TimeVaryingDetection_mrmr

### 2024-11-21 code/R/54188_ClassicCustomComparison_mrmr.Rmd
add code to interpret LOO comparison

with mrmr's built-in plotting functionality.

@@

Axes are not standardized, which limits comparison value.

@@

The loo( ) function generates an expected log predictive density (elpd) value for each model. The loo_compare( ) function ranks models based on their elpd values and calculates the difference in those values. A difference of 2-3x the standard error is generally considered significant in a LOO comparison. In this case, the elpd_diff value is 2.95x the standard error, suggesting that the custom mrmr model fits the Trapdoor data significantly better than the classic model.

@@

>>>>

...with mrmr's built-in plotting functionality.

@@

Note that axes are not standardized.

@@

The loo( ) function generates an expected log predictive density (elpd) value for each model. The loo_compare( ) function ranks models based on their elpd values, with the best fit listed first, and calculates the difference in those values. A difference of 2-3x the standard error is generally considered significant in a LOO comparison.

@@

# extract elpd_diff and se_diff for model1
elpd_diff_model1 <- loo_compare["model1", "elpd_diff"]
se_diff_model1 <- loo_compare["model1", "se_diff"]

# calculate significance ratio
result <- elpd_diff_model1 / se_diff_model1

# interpret
if (abs(result) > 2) {
  cat("Result of elpd_diff / se_diff for model1:", result, "\n")
  cat("The custom model fits the data significantly better than the classic model.\n")
} else {
  cat("Result of elpd_diff / se_diff for model1:", result, "\n")
  cat("The custom model does not fit the data significantly better than the classic model.\n")
}
